Calculating Entropies With Nested Sampling

### 2017-03-03 paper/ms.tex
Notation
Final results for sinusoid (even)

@@

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for each of the three
runs. The {\todo interim} results are:
\begin{align}
H_{\tau}    &= 7.307 \pm 0.027 \\
H_{\d}      &= 905.5 \pm 5.6   \\
H_{\tau,\d} &= 883.6 \pm 5.2
\end{align}

To conver these to differential entropies, I applied the log-volume
correction factors for 1, 101, and 102 dimensions, which are
$-6.215$, $-790.32$, and $-798.62$ respectively. This gives
the following {\todo interim} values for the differential entropies:
\begin{align}
H'_{\tau}     &= 1.092 \pm 0.027 \label{eqn:h_tau}\\
H'_{\d}       &= 115.2 \pm 5.6   \\
H'_{\tau, \d} &=  93.3 \pm 5.2   \label{eqn:h_joint}
\end{align}
The mutual information is equal to $H_{\tau} + H_{\d} - H_{\tau, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\tau, \d}$ if computed from the results
in Equations~\ref{eqn:h_tau} to~\ref{eqn:h_joint}. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
The resulting {\todo provisional} mutual information is
$I_{\tau, \d} = 31.7 \pm 3.8$ nats.

>>>>

I prefer to write the entropy of $x$ as $H_x$ rather than $H(x)$
(or $H(X)$ as is often seen), because the latter can wrongly imply that
the entropy is a property of the value of $x$ itself, rather than
our probability distribution for it.

@@

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for each of the three
runs. The results are:
\begin{align}
H_{\tau}    &= 7.307 \pm 0.027 \\
H_{\d}      &= 900.6 \pm 1.1   \\
H_{\tau,\d} &= 882.2 \pm 1.1
\end{align}

To conver these to differential entropies, I applied the log-volume
correction factors for 1, 101, and 102 dimensions, which are
$-6.215$, $-790.32$, and $-798.62$ respectively. This gives
the following values for the differential entropies:
\begin{align}
H'_{\tau}     &= 1.092 \pm 0.027 \label{eqn:h_tau}\\
H'_{\d}       &= 110.3 \pm 1.1   \\
H'_{\tau, \d} &=  83.6 \pm 1.1   \label{eqn:h_joint}
\end{align}
The mutual information is equal to $H_{\tau} + H_{\d} - H_{\tau, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\tau, \d}$ if computed from the results
in Equations~\ref{eqn:h_tau} to~\ref{eqn:h_joint}. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
The resulting  mutual information is
$I_{\tau, \d} = 27.85 \pm 0.83$ nats.
